The Influence of Connectivity on Dung Beetle Communities

### 2025-07-14 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
add ridiculous grad school required ch1 and ch3

\begin{center}
CHAPTER 1\\  
THE INFLUENCE OF CONNECTIVITY ON DUNG BEETLE COMMUNITIES\\  
\end{center}

@@

Moving forward, there is a bounty of knowledge yet to be collected for dung beetles in the south eastern United States. Relative to what is already known in tropical ecosystems, this study provides a glimpse on how dung beetles are responding to fragmentation and connectivity in subtropic pine habitats, but much can still be learned about dung beetles in these spaces and the role they play in ecosystems as well as how they interact with landscapes. The unique role of dung beetles as waste removers is fascinating enough and of great importance for maintaining landscapes so dominated by pastures like Southern US [@cheng_dweller_2022; @WOS:000368243300001]. Not only waste removal but also secondary effect such as seed dispersal and parasitic reduction are important to understand in the context of fragmentation [@fincher_effects_1975; @vulinec_dung_2002]. SRS provides an excellent experimental design for direct comparison of landscapes but another main goal of the site is to study dispersal, dung beetles would be an excellent system for studying movement. They already show promise, in preliminary trials I released beetles from both the connected and rectangular patches with baited traps in the central patch. I recovered one recapture which originated from the connected patch, indicating that individuals do move through corridors.

>>>>

\begin{center}
CHAPTER 1\\  
INTRODUCTION\\  
\end{center}

Corridors have been shown to be an important mechanism for facilitating the movement of organisms through fragmented landscapes [@haddad_corridor_2003]. These movements are hypothesized to prevent species diversity from declining in fragments, as well as help maintain the ecosystem services provided by these species (at both the patch- and landscape-level)[@burt_ants_2022]. Although there is some evidence that animals disperse between patches via corridors, and that connected patches have higher species diversity than unconnected ones, little work to date has investigated the consequences of these corridor-driven patterns for ecosystem services.

\begin{center}
CHAPTER 2\\  
THE INFLUENCE OF CONNECTIVITY ON DUNG BEETLE COMMUNITIES\\  
\end{center}

@@

\begin{center}
CHAPTER 3\\  
CONCLUSIONS AND FUTURE DIRECTIONS\\  
\end{center}

\doublespacing 
Moving forward, there is a bounty of knowledge yet to be collected for dung beetles in the south eastern United States. Relative to what is already known in tropical ecosystems, this study provides a glimpse on how dung beetles are responding to fragmentation and connectivity in subtropic pine habitats, but much can still be learned about dung beetles in these spaces and the role they play in ecosystems as well as how they interact with landscapes. The unique role of dung beetles as waste removers is fascinating enough and of great importance for maintaining landscapes so dominated by pastures like Southern US [@cheng_dweller_2022; @WOS:000368243300001]. Not only waste removal but also secondary effect such as seed dispersal and parasitic reduction are important to understand in the context of fragmentation [@fincher_effects_1975; @vulinec_dung_2002]. SRS provides an excellent experimental design for direct comparison of landscapes but another main goal of the site is to study dispersal, dung beetles would be an excellent system for studying movement. They already show promise, in preliminary trials I released beetles from both the connected and rectangular patches with baited traps in the central patch. I recovered one recapture which originated from the connected patch, indicating that individuals do move through corridors.
